Spectroscopic confirmation of very-wide binaries and large-separation comoving stars from \textsl{Gaia DR1}

### 2017-07-09 paper/comoving-followup.tex
add names

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{separation-hist.pdf}
  \end{center}
  \caption{%
    \emph{Left}: Distribution of point estimates of the 3D spatial separation of
    the stars in all observed comoving star pairs (gray), and only those
    identified as genuinely comoving (black). Note that the contamination rate
    is $\approx 60\%$ at large separations ($>1~\pc$), but there are still a
    significant number of genuine comoving pairs at these very wide separations.
    \emph{Right}: Distribution of sky separations of all comoving star pairs
    (gray) and only those identified as genuinely comoving (black).
    \label{fig:separation}}
\end{figure}

@@

\todo{Highlight the G subgiant-A pair}
\todo{Highlight a binary sequence-main sequence pair}
\todo{Highlight the largest mag difference MS pair}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{separation-hist-rave.pdf}
  \end{center}
  \caption{%
    \emph{Left}: Distribution of point estimates of the 3D spatial separation of
    the stars in all observed comoving star pairs (gray), and only those
    identified as genuinely comoving (black). Note that the contamination rate
    is $\approx 60\%$ at large separations ($>1~\pc$), but there are still a
    significant number of genuine comoving pairs at these very wide separations.
    \emph{Right}: Distribution of sky separations of all comoving star pairs
    (gray) and only those identified as genuinely comoving (black).
    \label{fig:separation}}
\end{figure}

>>>>

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{separation-hist.pdf}
  \end{center}
  \caption{%
    \emph{Left}: Distribution of point estimates of the 3D spatial separation of
    the stars in all observed comoving star pairs (gray), and only those
    identified as genuinely comoving (black). Note that the contamination rate
    is $\approx 60\%$ at large separations ($>1~\pc$), but there are still a
    significant number of genuine comoving pairs at these very wide separations.
    \emph{Right}: Distribution of chord lengths (tangential separations) for all
    comoving star pairs (gray) and only those identified as genuinely comoving
    (black).
    Noise in the parallax measurements makes the 3D separation distribution
    appear roughly uniform.
    Even the distribution in chord length appears to be approximately linear for
    large separations ($\gtrsim 0.1~\pc$).
    \label{fig:separation}}
\end{figure}

@@

We naively expect that comoving, coeval stars should lie along lines parallel to
the main sequence in color-magnitude space. The majority of our star pairs
appear to follow this expectation, with the exception of a few visible outliers.
For example, there appear to be at least a few main-sequence--giant-branch
pairs, and a few pairs that appear to cross the main-sequence.
We highlight a few of these pairs below.

\subsubsection{HD 95088 \& HD 92278}

\todo{Highlight the G subgiant-A pair}

\subsubsection{TYC 2486-1699-1 \& TYC 2477-430-1}

\todo{Highlight a binary sequence-main sequence pair}

\subsubsection{TYC 3792-658-1 \& HD 54318}

\todo{Highlight the largest mag difference MS pair}

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{separation-hist-rave.pdf}
  \end{center}
  \caption{%
    Same as \figurename~\ref{fig:separation}, but for our sample of genuine
    comoving stars combined with all genuine comoving stars identified from the
    RAVE overlap.
    \label{fig:separation-RAVE}}
\end{figure}
